Papers

### 2023-02-03 quarto/index.qmd
update

@@

* M. S. Bari, **A. Zhang**, S. Zheng, X. Shi, Y. Zhu, S. Joty, and M. Li<br>
	<a href="https://arxiv.org/abs/2212.10929" target="_blank">
	SPT: Semi-Parametric Prompt Tuning for Multitask Prompted Learning</a><br>
	*"If your prompt tuning can't converge easily, make it semi-parametric."*
	In *arXiv*, 2022<br>
	<a href="https://twitter.com/astonzhangAZ/status/1605959819894349824" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>

>>>>

* Z. Zhang, **A. Zhang**, M. Li, H. Zhao, G. Karypis, and A. J. Smola<br>
	<a href="https://arxiv.org/abs/2302.00923" target="_blank">Multimodal Chain-of-Thought Reasoning in Language Models</a><br>
	*"SOTA and surpassing human performance on the ScienceQA benchmark."*
	In *arXiv*, 2023<br>
	<a href="https://twitter.com/arankomatsuzaki/status/1621323705686134788" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
	<a href="https://github.com/amazon-science/mm-cot" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

@@

* M. S. Bari, **A. Zhang**, S. Zheng, X. Shi, Y. Zhu, S. Joty, and M. Li<br>
	<a href="https://arxiv.org/abs/2212.10929" target="_blank">
	SPT: Semi-Parametric Prompt Tuning for Multitask Prompted Learning</a><br>
	*"If your prompt tuning can't converge easily, make it semi-parametric."*
	In *arXiv*, 2023<br>
	<a href="https://twitter.com/astonzhangAZ/status/1605959819894349824" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
